Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-06-30 latex/paper.tex
added sequential alg for hiernmf2

\begin{algorithm}
\caption{Rank-2 Nonnegative Least Squares Solve}
\label{alg:r2nmf}
\begin{algorithmic}[1]
	\Require{$\M{C}$ is $n\times 2$ and $\M{G}$ is $2\times 2$ and s.p.d.}
	\Function{$\M{H} =$ Rank2-NLS-Solve}{$\M{C},\M{G}$}
		\State $\M{H} = \M{C}\M{G}^{-1}$
		\For{$i=1$ to $n$}
			\If{$\ME{H}{i1} < 0$ or $\ME{H}{i2} < 0$}
				\If{$\ME{H}{i1} \sqrt{\ME{G}{11}}  < \ME{H}{i2} \sqrt{\ME{G}{22}} $}
					\State $\ME{H}{i1} = 0$
					\State $\ME{H}{i2} = \ME{C}{i2} / \ME{G}{22}$
				\Else
					\State $\ME{H}{i1} = \ME{C}{i1} / \ME{G}{11}$
					\State $\ME{H}{i2} = 0$
				\EndIf
			\EndIf
		\EndFor
	\EndFunction
	\Ensure{$\displaystyle \M{H} = \argmin_{\M[\bar]{H} \geq \M{0}} \|\M{A}-\M{W}\M[\bar]{H}^\Tra\|$ is $n\times 2$ with $\M{C}=\M{A}^\Tra \M{W}$ and $\M{G}=\M{W}^\Tra\M{W}$}
\end{algorithmic}
\end{algorithm}

@@

>>>>

\begin{algorithm}
\caption{Rank-2 Nonnegative Least Squares Solve \cite{KP13}}
\label{alg:r2nmf}
\begin{algorithmic}[1]
	\Require{$\M{C}$ is $n\times 2$ and $\M{G}$ is $2\times 2$ and s.p.d.}
	\Function{$\M{H} =$ Rank2-NLS-Solve}{$\M{C},\M{G}$}
		\State $\M{H} = \M{C}\M{G}^{-1}$
		\For{$i=1$ to $n$}
			\If{$\ME{H}{i1} < 0$ or $\ME{H}{i2} < 0$}
				\If{$\ME{H}{i1} \sqrt{\ME{G}{11}}  < \ME{H}{i2} \sqrt{\ME{G}{22}} $}
					\State $\ME{H}{i1} = 0$
					\State $\ME{H}{i2} = \ME{C}{i2} / \ME{G}{22}$
				\Else
					\State $\ME{H}{i1} = \ME{C}{i1} / \ME{G}{11}$
					\State $\ME{H}{i2} = 0$
				\EndIf
			\EndIf
		\EndFor
	\EndFunction
	\Ensure{$\displaystyle \M{H} = \argmin_{\M[\bar]{H} \geq \M{0}} \|\M{A}-\M{W}\M[\bar]{H}^\Tra\|$ is $n\times 2$ with $\M{C}=\M{A}^\Tra \M{W}$ and $\M{G}=\M{W}^\Tra\M{W}$}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\caption{Hierarchical Clustering via Rank-2 NMF}
\label{alg:hiernmf2}
\begin{algorithmic}[1]
	\Require{$\M{A}$ is $m\times n$, $k$ is target number of leaves}
	\Function{${\cal T} =$ Hier-R2-NMF}{$\M{A}$}
		\State ${\cal R} = \text{node}(\M{A})$ \hfill \Comment{create root node}
		\State inject$({\cal Q},{\cal R})$ \hfill \Comment{create priority queue of leaves}
		\While{leaves$({\cal T}) < k$}
			\State ${\cal N} = \text{deleteMax}({\cal Q})$ \hfill \Comment{get leaf with max score}
			\State $[\M{W},\M{H}] = \textsc{Rank2-NMF}({\cal N}.\M{A})$ \hfill \Comment{split $\cal N$}
			\State partition ${\cal N}.\M{A}$ into $\M{A}_1$ and $\M{A}_2$ using $\M{H}$
			\State ${\cal N}_1 = \text{node}(\M{A}_1,\text{score}(\M{A}_1),\V{W}_1)$ \hfill \Comment{left child}
			\State ${\cal N}_2 = \text{node}(\M{A}_2,\text{score}(\M{A}_2),\V{W}_2)$ \hfill \Comment{right child}
			\State ${\cal N}.\text{left} = {\cal N}_1$, ${\cal N}.\text{right} = {\cal N}_2$
			\State inject$({\cal Q},{\cal N}_1)$, inject$({\cal Q},{\cal N}_2)$ 
		\EndWhile
	\EndFunction
	\Ensure{$\cal{T}$ is binary tree with $k$ leaves, each node has subset of columns of $\M{A}$ and feature vector $\V{w}$}
\end{algorithmic}
\end{algorithm}
